Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-05-29 bCFT_paper.tex
[draft] ML grant number added.

\begin{acknowledgments}
\todo[inline]{Mao: funding number?}
We are grateful for the discussion and suggestions provided by Thomas Faulkner, Xueda Wen, Shinsei Ryu, Michael Stone, Taylor Hughes and Romain Vasseur during the course of this research. 
TZ is supported by the National Science Foundation under grant number NSF-DMR-1306011.
This work made use of the Illinois Campus Cluster, a computing resource that is operated by the Illinois Campus Cluster Program (ICCP) in conjunction with the National Center for Supercomputing Applications (NCSA) and which is supported by funds from the University of Illinois at Urbana-Champaign.
\end{acknowledgments}

>>>>

\begin{acknowledgments}
We are grateful for the discussion and suggestions provided by Thomas Faulkner, Xueda Wen, Shinsei Ryu, Michael Stone, Taylor Hughes and Romain Vasseur during the course of this research. 
TZ is supported by the National Science Foundation under grant number NSF-DMR-1306011.
M.L. is supported by US NSF under grant DMR 1351895-CAR and US NSF Emerging Frontiers in Research and Innovation grant EFMA-1627184
This work made use of the Illinois Campus Cluster, a computing resource that is operated by the Illinois Campus Cluster Program (ICCP) in conjunction with the National Center for Supercomputing Applications (NCSA) and which is supported by funds from the University of Illinois at Urbana-Champaign.
\end{acknowledgments}
